How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-31 tse-paper/content.tex
Add TODO
start on new structure in introduction

At the moment there is only anecdotal evidence on the performance of these techniques and on when a technique should be preferred over other alternatives.
Developers and researches currently have little support when choosing which technique to use for a task.

The goal of this article is to investigate different chunk retrieval techniques for build logs and describe under which circumstances certain techniques can be recommended over others.
We aim to characterize different chunk retrieval techniques.
For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.

We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (CTS), and
  \item keyword search (KWS), an ad-hoc method for finding fitting passages by searching the whole text for the occurrence of a specific trigger word.
\end{itemize}
% TODO: Shortly describe each of these techniques

>>>>

\dots

build logs valuable data source, but semi-structured and verbose,
therefore need (automated) processing

To gain an impression on how researchers are using information from build logs
within their research and how they are gathering chunks from them to support
developers in understanding build outcomes, we conducted a systematic mapping
study.
Our goal was to classify how and what for researchers use build logs as a source
of data (\textbf{RQ1}).

The outcomes of our study shows that there are various attempts to retrieve
specific information from buildlogs. The resulting implementations are rarely
available and therefore rarely reused. Because of the high development overhead
of the custom parsers, many implementations are limited to small number of supported
build tools.

To address this, we implement three promising techniques for build log analysis.
They retrieve specific chunks of targeted information and are configured by
examples provided by the user.
We conduct an empirical study on the \emph{LogChunks} \todo{cite} data set to
gauge the performance of these chunk retrieval techniques and characterize
when one of the techniques should be preferred over other alternatives (\textbf{RQ2}).

% At the moment there is only anecdotal evidence on the performance of these
% techniques and on when a technique should be preferred over other alternatives.
% Developers and researches currently have little support when choosing which
% technique to use for a task.

% The goal of this article is to investigate different chunk retrieval techniques
% for build logs and describe under which circumstances certain techniques can be
% recommended over others.
% We aim to characterize different chunk retrieval techniques.
% For \textbf{Research Question 1} (\textbf{RQ1}), we analyze which criteria
% influence the suitability of a chunk retrieval technique for CI build logs.

We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item \textbf{Program Synthesis by Example (referred to as PBE)}
  Based on 
  \item \textbf{a common text similarity approach (CTS)}
  \item \textbf{keyword search (KWS), an ad-hoc method for finding fitting passages by searching the whole text for the occurrence of a specific trigger word}
\end{itemize}
% TODO: Shortly describe each of these techniques
